---
title: "Effect of $\\beta$-blockade on reproducibility of heart rate, oxygen uptake and work rate across repeated bouts of short-duration perceptually regulated exercise"
author: "Braden L. Mitchell, Ph.D."
output:
  pdf_document:
    number_sections: true
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, comment = NA)
options(tibble.print_max = Inf)
```

# Data preparation

```{r libraries}
library(dplyr)
library(tidyr)
library(lme4)      # v1.1.35.5
library(lmerTest)  # v3.1.3
library(emmeans)   # v1.10.5
library(irr)       # v0.84.1
```

```{r mets_function}
# Function to calculate METs using ACSM metabolic equation for treadmill running
calculate_mets <- function(speed, grade) {
  (3.5 + (0.2 * (speed * (1000 / 60))) + 
     (0.9 * (speed * (1000 / 60)) * (grade / 100))) / 3.5
}
```

```{r load_data}
# Load intervals data
intervals <- read.csv("../../Data/RPE_Intervals.csv")

# Load GXT outcomes data
gxt <- read.csv("../../Data/GXT_outcomes.csv") %>% 
  mutate(mets_peak = calculate_mets(speed_peak, grade_peak)) %>% 
  select(pid, condition, vo2kg_vt, hr_vt, vo2kg_peak, hr_peak, mets_peak) %>% 
  filter(pid %in% unique(intervals$pid))

# Load resting CV measures data
rest_cv <- read.csv("../../Data/RestingCV_final.csv") %>% 
  select(pid, condition, hr_60, sbp_60, dbp_60, spo2_60) %>% 
  filter(pid %in% unique(intervals$pid))
```

```{r prepare_intervals_data}
# Prepare intervals data
intervals <- intervals %>% 
  left_join(gxt, by = c("pid", "condition")) %>% 
  # Define condition & intensity as factors
  mutate(
    condition = factor(condition, c(0, 1), c("control", "bblockade")),
    intensity = factor(intensity, c(13, 15), c("rpe13", "rpe15"))
  ) %>% 
  # Calculate secondary variables
  mutate(
    mets = calculate_mets(speed, grade),
    pct_vo2kg_vt = (vo2kg / vo2kg_vt) * 100,
    pct_vo2kg_peak = (vo2kg / vo2kg_peak) * 100,
    pct_hr_vt = (hr / hr_vt) * 100,
    pct_hr_peak = (hr / hr_peak) * 100,
    pct_mets_peak = (mets / mets_peak) * 100,
  )
```

# Preliminary analyses

```{r pivot_rest_cv}
# Transform resting CV measures to wide format
rest_cv_wide <- rest_cv %>% 
  mutate(condition = factor(condition, c(0, 1), c("control", "bblockade"))) %>%
  pivot_wider(names_from = condition, values_from = c(hr_60:spo2_60))
```

```{r, pivot_gxt_data}
# Transform GXT outcomes to wide format
gxt_wide <- gxt %>% 
  mutate(condition = factor(condition, c(0, 1), c("control", "bblockade"))) %>%
  pivot_wider(names_from = condition, values_from = c(vo2kg_vt:mets_peak))
```

## Difference in resting cardiovascular measures between conditions

```{r ttest_hr_rest}
# Difference in resting HR, B-blockade vs. Control
t.test(rest_cv_wide$hr_60_bblockade, rest_cv_wide$hr_60_control, paired = TRUE)
```

```{r ttest_sbp_rest}
# Difference in resting systolic BP, B-blockade vs. Control
t.test(rest_cv_wide$sbp_60_bblockade, rest_cv_wide$sbp_60_control, paired = TRUE)
```

```{r ttest_dbp_rest}
# Difference in resting diastolic BP, B-blockade vs. Control
t.test(rest_cv_wide$dbp_60_bblockade, rest_cv_wide$dbp_60_control, paired = TRUE)
```

```{r ttest_spo2_rest}
# Difference in resting SpO2, B-blockade vs. Control
t.test(rest_cv_wide$spo2_60_bblockade, rest_cv_wide$spo2_60_control, paired = TRUE)
```

## Difference in exercise responses between conditions

```{r ttest_vo2kg_vt}
# Difference in VO2kg @ VT, B-blockade vs. Control
t.test(gxt_wide$vo2kg_vt_bblockade, gxt_wide$vo2kg_vt_control, paired = TRUE)
```

```{r ttest_vo2kg_peak}
# Difference in peak VO2kg, B-blockade vs. Control
t.test(gxt_wide$vo2kg_peak_bblockade, gxt_wide$vo2kg_peak_control, paired = TRUE)
```

```{r ttest_hr_vt}
# Difference in HR @ VT, B-blockade vs. Control
t.test(gxt_wide$hr_vt_bblockade, gxt_wide$hr_vt_control, paired = TRUE)
```

```{r ttest_hr_peak}
# Difference in peak HR, B-blockade vs. Control
t.test(gxt_wide$hr_peak_bblockade, gxt_wide$hr_peak_control, paired = TRUE)
```

```{r ttest_mets_peak}
# Difference in peak work rate (METs), B-blockade vs. Control
t.test(gxt_wide$mets_peak_bblockade, gxt_wide$mets_peak_control, paired = TRUE)
```

# Linear mixed-effects models

## Heart rate

```{r lmm_fit_hr_full}
# Fit fully specified model for heart rate
lmm_hr_full <- lmer(
  hr ~ condition * intensity * bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_fit_hr_reduced}
# Fit reduced model for heart rate without second-order interaction
lmm_hr_reduced <- lmer(
  hr ~ condition + intensity + bout_rpe + condition:intensity + 
    condition:bout_rpe + intensity:bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_anova_hr}
# Compare models via likelihood ratio test
anova(lmm_hr_full, lmm_hr_reduced)
```

```{r}
summary(lmm_hr_reduced)
confint(lmm_hr_reduced)
```

```{r}
# Pairwise comparisons for condition * intensity
emmeans(lmm_hr_reduced, pairwise ~ condition * intensity)
```

```{r}
# Planned contrasts between conditions within intensity
summary(
  emmeans(lmm_hr_reduced, pairwise ~ condition | intensity),
  infer = TRUE
)
```

```{r lmm_diagnostics_hr}
plot(lmm_hr_reduced)

qqnorm(residuals(lmm_hr_reduced))
qqline(residuals(lmm_hr_reduced))
```

## %HRpeak

```{r lmm_fit_pcthrpeak_full}
# Fit fully specified model for %HRpeak
lmm_pcthrpeak_full <- lmer(
  pct_hr_peak ~ condition * intensity * bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_fit_pcthrpeak_reduced}
# Fit reduced model for %HRpeak without second-order interaction
lmm_pcthrpeak_reduced <- lmer(
  pct_hr_peak ~ condition + intensity + bout_rpe + condition:intensity + 
    condition:bout_rpe + intensity:bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_anova_pcthrpeak}
# Compare models via likelihood ratio test
anova(lmm_pcthrpeak_full, lmm_pcthrpeak_reduced)
```

```{r}
summary(lmm_pcthrpeak_reduced)
confint(lmm_pcthrpeak_reduced)
```

```{r}
# Planned contrasts between conditions within intensity
summary(
  emmeans(lmm_pcthrpeak_reduced, pairwise ~ condition | intensity),
  infer = TRUE
)
```

```{r lmm_diagnostics_pcthrpeak}
plot(lmm_pcthrpeak_reduced)

qqnorm(residuals(lmm_pcthrpeak_reduced))
qqline(residuals(lmm_pcthrpeak_reduced))
```

## Oxygen uptake

```{r lmm_fit_vo2kg_full}
# Fit fully specified model for oxygen uptake
lmm_vo2kg_full <- lmer(
  vo2kg ~ condition * intensity * bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_fit_vo2kg_reduced}
# Fit reduced model for VO2kg without second-order interaction
lmm_vo2kg_reduced <- lmer(
  vo2kg ~ condition + intensity + bout_rpe + condition:intensity + 
    condition:bout_rpe + intensity:bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_anova_vo2kg}
# Compare models via likelihood ratio test
anova(lmm_vo2kg_full, lmm_vo2kg_reduced)
```

```{r}
summary(lmm_vo2kg_reduced)
confint(lmm_vo2kg_reduced)
```

```{r}
# Planned contrasts between conditions within intensity
summary(
  emmeans(lmm_vo2kg_reduced, pairwise ~ condition | intensity),
  infer = TRUE
)
```

```{r lmm_diagnostics_vo2kg}
plot(lmm_vo2kg_reduced)

qqnorm(residuals(lmm_vo2kg_reduced))
qqline(residuals(lmm_vo2kg_reduced))
```

## %VO2peak

```{r lmm_fit_pctvo2kgpeak_full}
# Fit fully specified model for %VO2peak
lmm_pctvo2kgpeak_full <- lmer(
  pct_vo2kg_peak ~ condition * intensity * bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_fit_pctvo2kgpeak_reduced}
# Fit reduced model for %VO2peak without second-order interaction
lmm_pctvo2kgpeak_reduced <- lmer(
  pct_vo2kg_peak ~ condition + intensity + bout_rpe + condition:intensity + 
    condition:bout_rpe + intensity:bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_anova_pctvo2kgpeak}
# Compare models via likelihood ratio test
anova(lmm_pctvo2kgpeak_full, lmm_pctvo2kgpeak_reduced)
```

```{r}
summary(lmm_pctvo2kgpeak_reduced)
confint(lmm_pctvo2kgpeak_reduced)
```

```{r}
# Planned contrasts between conditions within intensity
summary(
  emmeans(lmm_pctvo2kgpeak_reduced, pairwise ~ condition | intensity),
  infer = TRUE
)
```

```{r lmm_diagnostics_pctvo2kgpeak}
plot(lmm_pctvo2kgpeak_reduced)

qqnorm(residuals(lmm_pctvo2kgpeak_reduced))
qqline(residuals(lmm_pctvo2kgpeak_reduced))
```

## Work rate (METs)

```{r lmm_fit_mets_full}
# Fit fully specified model for METs
lmm_mets_full <- lmer(
  mets ~ condition * intensity * bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_fit_mets_reduced}
# Fit reduced model for METs without second-order interaction
lmm_mets_reduced <- lmer(
  mets ~ condition + intensity + bout_rpe + condition:intensity + 
    condition:bout_rpe + intensity:bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_anova_mets}
# Compare models via likelihood ratio test
anova(lmm_mets_full, lmm_mets_reduced)
```

```{r}
summary(lmm_mets_reduced)
confint(lmm_mets_reduced)
```

```{r}
# Planned contrasts between conditions within intensity
summary(
  emmeans(lmm_mets_reduced, pairwise ~ condition | intensity),
  infer = TRUE
)
```

```{r lmm_diagnostics_mets}
plot(lmm_mets_reduced)

qqnorm(residuals(lmm_mets_reduced))
qqline(residuals(lmm_mets_reduced))
```

## %WRpeak (%METpeak)

```{r lmm_fit_pctmetspeak_full}
# Fit fully specified model for %METpeak
lmm_pctmetspeak_full <- lmer(
  pct_mets_peak ~ condition * intensity * bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_fit_pctmetspeak_reduced}
# Fit reduced model for %METpeak without second-order interaction
lmm_pctmetspeak_reduced <- lmer(
  pct_mets_peak ~ condition + intensity + bout_rpe + condition:intensity + 
    condition:bout_rpe + intensity:bout_rpe + (1 | pid),
  data = intervals
)
```

```{r lmm_anova_pctmetspeak}
# Compare models via likelihood ratio test
anova(lmm_pctmetspeak_full, lmm_pctmetspeak_reduced)
```

```{r}
summary(lmm_pctmetspeak_reduced)
confint(lmm_pctmetspeak_reduced)
```

```{r}
# Planned contrasts between conditions within intensity
summary(
  emmeans(lmm_pctmetspeak_reduced, pairwise ~ condition | intensity),
  infer = TRUE
)
```

```{r lmm_diagnostics_pctmetspeak}
plot(lmm_pctmetspeak_reduced)

qqnorm(residuals(lmm_pctmetspeak_reduced))
qqline(residuals(lmm_pctmetspeak_reduced))
```

# Intraclass Correlations

```{r}
# Transform intervals data to wide format
intervals_wide <- intervals %>%
  select(-c(bout_session, speed:mets_peak)) %>%
  pivot_wider(
    names_from = c(condition, intensity, bout_rpe),
    values_from = c(hr, pct_hr_vt, pct_hr_peak, vo2kg, pct_vo2kg_vt,
                    pct_vo2kg_peak, mets, pct_mets_peak),
    names_glue = "{gsub('_', '', .value)}_{condition}_{intensity}_{bout_rpe}"
  )
```

```{r}
fisherz_compare <- function(icc_control, icc_bblockade) {
  fisher_z <- function(icc) {
    0.5 * log((1 + icc) / (1 - icc))
  }
  
  z_control <- fisher_z(icc_control$value)
  z_bblockade  <- fisher_z(icc_bblockade$value)
  
  z_diff <- z_control - z_bblockade
  se_diff <- sqrt(2 / (icc_control$subjects - 3))
  
  z_score  <- z_diff / se_diff
  p_value <- 2 * (1 - pnorm(abs(z_score)))
  
  return(
    list("z_diff" = z_diff, "z_score" = z_score, "p_value" = p_value)
  )
}
```

## Heart rate

```{r}
# ICC for Control, RPE 13
icc_hr_control_13 <- intervals_wide %>% 
  select(hr_control_rpe13_1:hr_control_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_hr_control_13
```

```{r}
# ICC for B-blockade, RPE 13
icc_hr_bblockade_13 <- intervals_wide %>% 
  select(hr_bblockade_rpe13_1:hr_bblockade_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_hr_bblockade_13
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_hr_control_13, icc_hr_bblockade_13)
```

```{r}
# ICC for Control, RPE 15
icc_hr_control_15 <- intervals_wide %>% 
  select(hr_control_rpe15_1:hr_control_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_hr_control_15
```

```{r}
# ICC for B-blockade, RPE 15
icc_hr_bblockade_15 <- intervals_wide %>% 
  select(hr_bblockade_rpe15_1:hr_bblockade_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_hr_bblockade_15
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_hr_control_15, icc_hr_bblockade_15)
```

## %HRpeak

```{r}
# ICC for Control, RPE 13
icc_pcthrpeak_control_13 <- intervals_wide %>% 
  select(pcthrpeak_control_rpe13_1:pcthrpeak_control_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_pcthrpeak_control_13
```

```{r}
# ICC for B-blockade, RPE 13
icc_pcthrpeak_bblockade_13 <- intervals_wide %>% 
  select(pcthrpeak_bblockade_rpe13_1:pcthrpeak_bblockade_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_pcthrpeak_bblockade_13
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_pcthrpeak_control_13, icc_pcthrpeak_bblockade_13)
```

```{r}
# ICC for Control, RPE 15
icc_pcthrpeak_control_15 <- intervals_wide %>% 
  select(pcthrpeak_control_rpe15_1:pcthrpeak_control_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_pcthrpeak_control_15
```

```{r}
# ICC for B-blockade, RPE 15
icc_pcthrpeak_bblockade_15 <- intervals_wide %>% 
  select(pcthrpeak_bblockade_rpe15_1:pcthrpeak_bblockade_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_pcthrpeak_bblockade_15
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_pcthrpeak_control_15, icc_pcthrpeak_bblockade_15)
```

## Oxygen uptake

```{r}
# ICC for Control, RPE 13
icc_vo2kg_control_13 <- intervals_wide %>% 
  select(vo2kg_control_rpe13_1:vo2kg_control_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_vo2kg_control_13
```

```{r}
# ICC for B-blockade, RPE 13
icc_vo2kg_bblockade_13 <- intervals_wide %>% 
  select(vo2kg_bblockade_rpe13_1:vo2kg_bblockade_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_vo2kg_bblockade_13
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_vo2kg_control_13, icc_vo2kg_bblockade_13)
```

```{r}
# ICC for Control, RPE 15
icc_vo2kg_control_15 <- intervals_wide %>% 
  select(vo2kg_control_rpe15_1:vo2kg_control_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_vo2kg_control_15
```

```{r}
# ICC for B-blockade, RPE 15
icc_vo2kg_bblockade_15 <- intervals_wide %>% 
  select(vo2kg_bblockade_rpe15_1:vo2kg_bblockade_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_vo2kg_bblockade_15
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_vo2kg_control_15, icc_vo2kg_bblockade_15)
```

## %VO2peak

```{r}
# ICC for Control, RPE 13
icc_pctvo2kgpeak_control_13 <- intervals_wide %>% 
  select(pctvo2kgpeak_control_rpe13_1:pctvo2kgpeak_control_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctvo2kgpeak_control_13
```

```{r}
# ICC for B-blockade, RPE 13
icc_pctvo2kgpeak_bblockade_13 <- intervals_wide %>% 
  select(pctvo2kgpeak_bblockade_rpe13_1:pctvo2kgpeak_bblockade_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctvo2kgpeak_bblockade_13
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_pctvo2kgpeak_control_13, icc_pctvo2kgpeak_bblockade_13)
```

```{r}
# ICC for Control, RPE 15
icc_pctvo2kgpeak_control_15 <- intervals_wide %>% 
  select(pctvo2kgpeak_control_rpe15_1:pctvo2kgpeak_control_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctvo2kgpeak_control_15
```

```{r}
# ICC for B-blockade, RPE 15
icc_pctvo2kgpeak_bblockade_15 <- intervals_wide %>% 
  select(pctvo2kgpeak_bblockade_rpe15_1:pctvo2kgpeak_bblockade_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctvo2kgpeak_bblockade_15
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_pctvo2kgpeak_control_15, icc_pctvo2kgpeak_bblockade_15)
```

## Work rate (METs)

```{r}
# ICC for Control, RPE 13
icc_mets_control_13 <- intervals_wide %>% 
  select(mets_control_rpe13_1:mets_control_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_mets_control_13
```

```{r}
# ICC for B-blockade, RPE 13
icc_mets_bblockade_13 <- intervals_wide %>% 
  select(mets_bblockade_rpe13_1:mets_bblockade_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_mets_bblockade_13
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_mets_control_13, icc_mets_bblockade_13)
```

```{r}
# ICC for Control, RPE 15
icc_mets_control_15 <- intervals_wide %>% 
  select(mets_control_rpe15_1:mets_control_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_mets_control_15
```

```{r}
# ICC for B-blockade, RPE 15
icc_mets_bblockade_15 <- intervals_wide %>% 
  select(mets_bblockade_rpe15_1:mets_bblockade_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_mets_bblockade_15
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_mets_control_15, icc_mets_bblockade_15)
```

## %WRpeak (%METpeak)

```{r}
# ICC for Control, RPE 13
icc_pctmetspeak_control_13 <- intervals_wide %>% 
  select(pctmetspeak_control_rpe13_1:pctmetspeak_control_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctmetspeak_control_13
```

```{r}
# ICC for B-blockade, RPE 13
icc_pctmetspeak_bblockade_13 <- intervals_wide %>% 
  select(pctmetspeak_bblockade_rpe13_1:pctmetspeak_bblockade_rpe13_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctmetspeak_bblockade_13
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_pctmetspeak_control_13, icc_pctmetspeak_bblockade_13)
```

```{r}
# ICC for Control, RPE 15
icc_pctmetspeak_control_15 <- intervals_wide %>% 
  select(pctmetspeak_control_rpe15_1:pctmetspeak_control_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctmetspeak_control_15
```

```{r}
# ICC for B-blockade, RPE 15
icc_pctmetspeak_bblockade_15 <- intervals_wide %>% 
  select(pctmetspeak_bblockade_rpe15_1:pctmetspeak_bblockade_rpe15_3) %>% 
  icc("twoway", "agreement", "single")

icc_pctmetspeak_bblockade_15
```

```{r}
# Fisher's z-transformation & z-test
fisherz_compare(icc_pctmetspeak_control_15, icc_pctmetspeak_bblockade_15)
```

# Coefficients of variation

```{r}
calculate_cv <- function(x) {
  (sd(x, na.rm = TRUE) / mean(x, na.rm = TRUE)) * 100
}
```

```{r}
intervals_cv <- intervals %>% 
  group_by(pid, condition, intensity) %>% 
  summarise(
    hr = calculate_cv(hr),
    vo2kg = calculate_cv(vo2kg),
    mets = calculate_cv(mets),
    .groups = "drop"
  ) 
```

```{r}
intervals_cv %>% 
  pivot_wider(
    names_from = c(condition, intensity),
    values_from = c(hr, vo2kg, mets)
  ) %>%
  pivot_longer(
    cols = !pid,
    names_to = "outcome",
    values_to = "cv"
  ) %>% 
  group_by(outcome) %>% 
  summarise(
    mean_cv = round(mean(cv, na.rm = TRUE), 1),
    sd_cv = round(sd(cv, na.rm = TRUE), 1),
    min_cv = round(min(cv, na.rm = TRUE), 1),
    max_cv = round(max(cv, na.rm = TRUE), 1)
  ) 
```

```{r}
# ANOVA
anova_hr_cv <- aov(
  hr ~ intensity * condition + Error(pid / (intensity * condition)),
  data = intervals_cv
)

summary(anova_hr_cv)
```

```{r}
# ANOVA
anova_vo2kg_cv <- aov(
  vo2kg ~ intensity * condition + Error(pid / (intensity * condition)),
  data = intervals_cv
)

summary(anova_vo2kg_cv)
```

```{r}
# ANOVA
anova_mets_cv <- aov(
  mets ~ intensity * condition + Error(pid / (intensity * condition)),
  data = intervals_cv
)

summary(anova_mets_cv)
```

